---
title: "Homework 1"
author: "Rebecca Seery"
format: pdf
---

# Iris dataset

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
data(iris)
```

The **Iris** dataset contains the measurements of 50 different flowers belonging to three different species of iris:

-   *Setosa*
-   *Versicolor*
-   *Virginica*

This data is available in Base R by using `data(iris)`.

The first few rows of the dataset are as follows:

```{r, message=FALSE, warning=FALSE, echo=FALSE}
knitr::kable(head(iris))
```

Here is a plot of two of the measures in the dataset: the *Sepal Length* and *Petal Length*. We can see that [*Setosa*]{style="color:red;"} is considerably separated from the other species [*Versicolor*]{style="color:green;"} and [*Virginica*]{style="color:blue;"}.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# Create a scatter plot using ggplot:
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Iris Data", 
       x = "Sepal Length (cm)", 
       y = "Petal Length (cm)")
```
